Fixing Vulnerabilities Potentially Hinders Maintainability

### 2021-02-09 response/response.tex

\end{revcomment}

\Us Thank you for your positive feedback on the paper presentation and replication
package.

We would like to rebut your concern about Better Code Hub (BCH)'s guidelines not 
being related to maintainability. First, as mentioned in the paper, BCH checks GitHub 
codebases against 10 engineering guidelines as devised by Software Improvement Group 
(SIG). These guidelines are the result of many years of experience: analyzing more 
than 15 million lines of code every week, SIG maintains the industry’s largest 
benchmark, containing more than 10 billion lines of code across 200+ technologies; SIG 
is, according to their website, the only lab in the world certified by TÜViT to issue ISO 25010:2011 
certificates for Trusted Product Maintainability\footnote{Information available here: 
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/}}.
TÜViT is an IT Security company. Being certified by TÜViT means 
that the company checked if BCH actually respects and follows the ISO 25010 guidelines.

Second, the relation of the entire set of
guidelines to maintainability is well detailed in the O'Reilly's book ``Building Maintainable 
Software: Ten Guidelines for Future-Proof Code'' by Professor Joost Visser
\footnote{Available here: 
\url{https://www.softwareimprovementgroup.com/resources/ebook-building-maintainable-software/}}.
In fact, the underlying maintainability model for BCH is documented with several
(non-academic) reports linked at this page:
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/} as 
well as validated by the academic community in the following paper:

@@

\end{revcomment}

\Us We kindly thank the reviewer for the comments.

As mentioned in the paper, BCH checks GitHub codebases against $10$ engineering 
guidelines as devised by Software Improvement Group (SIG). SIG has devised 
these guidelines after many years of experience: analyzing more than $15$ million 
lines of code every week, SIG maintains the industry’s largest 
benchmark, containing more than $10$ billion lines of code across $200$+ 
technologies; SIG is the only lab in the world certified by TÜViT to issue ISO 25010:2011
certificates for Trusted Product Maintainability\footnote{Information available here: 
\url{https://www.softwareimprovementgroup.com/methodologies/iso-iec-25010-2011-standard/}}.

% Each of the guidelines in isolation is easy to understand, but, when 
% combined and evaluated as a whole, it becomes easy to see why 
%they would comprise the definition of good software. 
Furthermore, the relation of the entire set of
guidelines to maintainability is well detailed in the O'Reilly's book ``Building Maintainable 
Software: Ten Guidelines for Future-Proof Code'' by Professor Joost Visser
\footnote{Available here: 
\url{https://www.softwareimprovementgroup.com/resources/ebook-building-maintainable-software/}}.

### 2021-02-09 response/response.tex

\begin{revcomment}[2.9]
    Section 3\\
    \begin{itemize}
        \item Please explain your repeatable methodology to "clean the dataset and select the most relevant and 
        compatible projects" (page 8, line 14) that brings the patches from 1282 to 969.  
        \item From 969 to 866 patches - 
        you just could not classify?  Please explain.
    \end{itemize}
\end{revcomment}

\Us As explained in comment $2.6$, the $1282$ commits refer only to the Ponta et al. dataset (a total of $624$ 
patches). In total, we analyzed $1300$ patches ($624$ patches from Ponta et al. and $676$ from Secbench). 
However, our study only considers $969$ patches. We detected a total of $23$ patches with floss-refactorings. 
In addition, BCH has some limitations, in particular, the lack of language support and project size,
and was uncapable of analyzing the rest of the $308$ data points. All of this is explained
in more detail later in Section 3.4.

\begin{quote}
    Security patches can be performed through one commit (single-commit); 
    several consecutive commits (multi-commits); or, commit(s) interleaved with more 
    programming activities (floss-refactoring). Only $10.7\%$ of the data points 
    of our dataset involve more than one commit, the other
    $89.3\%$ of the cases are single-commit patches. We manually 
    inspected $25.1\%$ ($244$/$969$) of the security patches---$122$ from each dataset---and, 
    identified a total of $23$ floss-refactorings. Many of these 
    are patches with many changes where it is hard to understand which parts 
    involve the security patch. These were disregarded to minimize the impact 
    of measuring other programming activities rather than solely security patches
    can have in our results.

    For projects with large codebases, the results calculated for 
    the \emph{Keep Your Codebase Small} guideline were way above the 
    limit set by BCH ($20$ Person-years). We suspect this threshold 
    may not be well calibrated. Thus, we decided not to consider 
    this guideline in our research. The 
    \emph{Automated Tests} guideline was also not considered since the 
    tool does not contemplate two of the most important techniques to 
    security testing: vulnerability scanning and penetration testing. 
    Instead, it only contemplates unit testing. In total, 
    we detected $308$ data points suffering from these two limitations. 
    Those data points were disregarded from the study.
\end{quote}

@@

We define floss-refactoring with the paragraph below. 
Regarding the methodology to detect floss-refactorings, 
we manually inspected $25.1\%$ ($244$/$969$) of the security 
patches---$122$ from each dataset---and, 
identified a total of $23$ floss-refactorings. We clarified 
this in the paper:

\begin{quote}
    Security patches can be performed through one commit (single-commit); 
    several consecutive commits (multi-commits); or, commit(s) interleaved with more 
    programming activities (floss-refactoring). Only $10.7\%$ of the data points 
    of our dataset involve more than one commit, the other
    $89.3\%$ of the cases are single-commit patches. We manually 
    inspected $25.1\%$ ($244$/$969$) of the security patches---$122$ from each dataset---and, 
    identified a total of $23$ floss-refactorings. Many of these 
    are patches with many changes where it is hard to understand which parts 
    involve the security patch. These were disregarded to minimize the impact 
    of measuring other programming activities rather than solely security patches
    can have in our results. 
\end{quote}

\begin{revcomment}[2.14]
    Section 3\\
    \begin{itemize}
        \item Page 11, Line 42 - I think you are saying you removed these two guidelines 
        from the analysis of all projects (as shown in Figure 4) but this paragraph seems 
        to say this was only for projects with large code bases.
    \end{itemize}
\end{revcomment}

\Us We started with all the guidelines but after analyzing the BCH results, 
we found that some of the results for the \emph{Keep Your Codebase Small} guideline 
were way above the limit set by BCH ($20$ Person-years). We suspect this threshold 
may not be well calibrated. Thus, we decided not to consider 
this guideline in our research. We did not want 
to lose more data points. Thus, we decided to not consider the guideline for all projects.

@@

We also did not consider the \emph{Automated Tests} guideline because
this guideline does not contemplate vulnerability scanning and penetration testing
which are the two most important testing techniques in security.

We improved the paper in the following paragraph:

\begin{quote}
    Due to BCH limitations, in particular, lack of language support 
    and project size by BCH, $308$ data points were not analyzed and automatically 
    disregarded from our study. After performing the BCH analysis and 
    performing the maintainability calculations, we found the following 
    limitations regarding two BCH's guidelines:

    1) For projects with large codebases, the results calculated for 
    the \emph{Keep Your Codebase Small} guideline were way above the 
    limit set by BCH ($20$ Person-years). We suspect this threshold 
    may not be well calibrated. Thus, we decided not to consider 
    this guideline in our research.

    2) The 
    \emph{Automated Tests} guideline was also not considered since the 
    tool does not contemplate two of the most important techniques to 
    security testing: vulnerability scanning and penetration testing. 
    Instead, it only contemplates unit testing. 
\end{quote}

@@

\begin{revcomment}[2.15]
    Section 3\\
    \begin{itemize}
        \item Page 11  line 48.  How many were disregarded?
    \end{itemize}
\end{revcomment}

\Us Due to BCH limitations, in particular, lack of language support 
and project size by BCH, $308$ data points were disregarded.
We clarified it in the paper (Section 3.4):

\begin{quotation}
    Due to BCH limitations, in particular, lack of language support 
    and project size by BCH, $308$ data points were not analyzed and automatically 
    disregarded from our study. 
\end{quotation}

### 2021-02-09 paper/emse20.tex
improving response and paper to the guidelines that were not considered

For projects with large codebases, the results retrieved for 
\emph{Keep Your Codebase Small} were not viable because they 
retrieved values above the limit set by BCH ($20$ Person-years). Thus, 
we decided to not consider this guideline in our research. The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
Instead, it only contemplates unit testing. Due to BCH limitations, 
we detected $308$ data points that retrieved incorrect overall 
calculations. Those data points were disregarded from the study.

>>>>

Due to BCH limitations, in particular, lack of language support 
and project size by BCH, $308$ data points were not analyzed and automatically 
disregarded from our study. After performing the BCH analysis and 
performing the maintainability calculations, we found the following 
limitations regarding two BCH's guidelines:

1) For projects with large codebases, the results calculated for 
the \emph{Keep Your Codebase Small} guideline were way above the 
limit set by BCH ($20$ Person-years). We suspect this threshold 
may not be well calibrated. Thus, we decided not to consider 
this guideline in our research.

2) The 
\emph{Automated Tests} guideline was also not considered since the 
tool does not contemplate two of the most important techniques to 
security testing: vulnerability scanning and penetration testing. 
Instead, it only contemplates unit testing.
